%%This is a very basic article template.
%%There is just one section and two subsections.
\documentclass{article}

\begin{document}


\section{Title}The Rise Of the Lagosians !

\subsection{Subtitle}

Plain text.this is the new Latex project. we shall surely get all things to be
working correctly.

\subsection{How it all started}How it all started. In this section, we =discuss
the factors that lead to the return of curroption in the empire and the rise of
CHristainaitry. In the aftermath of the slave trade, there arose the need to
prosecute the chief slave traders.
Let us now try makoing changes from the text editor- outside if eclipse---


\subsection{The Race for the Throne of the Oba of Lagos}. The
Aare Ona Kakanfo Of YorubaLand. the Emir of Ilorin



More plain text.


\subsection{ The Influence from the Benin Empire}.

the benin empire is acclaimed to have existed form a very long period ago. according to archealogical discoveries, the empire existed as far backa s the 17th century, making it one of the oldest in West Africa, following only after the Tuareg Arabs of the Sahara desert.

\subsection{ The Oba of Ore}. 

The Ore kingdom is believed to have emanated for the Benin Kingdom. There are very strong reasons why this kind of believe should be upheld, especially in the face of so much adversity. 

\subsection{ My PC Tests}. 

I am now testing the edployment om my PC, hope this works as it did on the office PC. The time to change habits is now.additional texts to the beginning opf the twentieth century. Testing from the office PC



\end{document}
